Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Slightly more text, for page balance

Maximum common subgraph problems arise in biology and chemistry
\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
\cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
designs \cite{DBLP:journals/jair/CookH94}, in character recognition problems \cite{SIWEILU1991617},
and in many other domains \cite{Shasha:2002:AAT:543613.543620}, both directly and as a way of
measuring the similarity or difference between two graphs
\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate two
variants of this problem in \cref{figure:mcsexample}.

>>>>

Maximum common subgraph problems arise in biology and chemistry
\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
\cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
designs \cite{DBLP:journals/jair/CookH94}, in character recognition problems \cite{SIWEILU1991617},
and in many other domains \cite{Shasha:2002:AAT:543613.543620}, both directly and as a way of
measuring the similarity or difference between two graphs
\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate two
variants of this problem in \cref{figure:mcsexample}---in both cases we are finding an induced
subgraph and maximising the number of vertices selected, but in the second variant the common
subgraph must be connected.
